Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-14 longoutput.tex
Start to rewrite measurement protocol
Finish 2nd draft for longoutput

Let $C$ be a circuit with the above properties. Define the following quantities.
\begin{itemize}
	\item $C=U_T\ldots U_1$
	\item Let $x$ be the circuit input. Which is classical.
	\item Let $y$ denote the initial state. That is, $x$ possibly concatenated with ancillaries.
	\item Let $y_i$ denote the $i$-th bit of $y$
	\item Let $n=|y|$ be the number of qubits in $C$
\end{itemize}

We then attempt to construct a local Hamiltonian with the following ground state that encodes the history of the computation: $$\psi_{circuit}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
We do so by ensuring states perpendicular to it have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification is taken from \cite{PhysRevA.78.012352}.

@@

Then, we ensure that the initial condition is set up correctly.
$$H_{in}=\sum_{i=1}^{|y|}(I-\ket{y_i}\bra{y_i})\otimes\ket{0}\bra{0}_1$$
The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$. Furthermore, $H_{in}\in\spn\mathcal{G}_{XZ}$
$$H_{in}=\frac{1}{4}\sum_{i=1}^{|y|}(I-(-1)^{y_i}Z_i)\otimes(I+Z_1)$$

@@

Now we combine the three Hamiltonians defined. First consider their kernels.
$$K_{clock}=\ker H_{clock}$$
$$K_{in}=\ker H_{in}$$
$$K_{prop}=\ker H_{prop}$$
Notice that (TODO need proof or no?)
$$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\psi_{circuit}}$$
We now define
$$K=(\spn\set{\psi_{circuit}})^\bot$$
and consider $H_{clock}\big|_K,H_{in}\big|_K,H_{prop}\big|_K$. That is, we restrict the following computations to the subspace $K$. We apply the projection lemma.
$$\exists J_{clock},
\lambda(H_{in}\big|_K+J_{clock}H_{clock}\big|_K)\geq
\lambda(H_{in}\big|_{K\cap K_{clock}})-\frac{1}{8}$$
$$\exists J_{prop},
\lambda(H_{in}\big|_K+J_{clock}H_{clock}\big|_K+J_{prop}H_{prop}\big|_K)\geq
\lambda(H_{in}\big|_{K\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_K)\geq\frac{3}{4}$$
So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$. It has the following properties.
\begin{itemize}
	\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
	\item $\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$ for $\ket\phi$ such that $\braket{\phi|\psi_{circuit}}=0$
	\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$
\end{itemize}

@@

Given $\ket\phi$, now we're interested in the value of $\braket{\phi|H|\phi}$. Here we follow \cite{PhysRevA.93.022326}. Note that if $\phi=\psi_{circuit}$, then $\braket{\phi|H|\phi}=0$. If $\braket{\phi|\psi_{circuit}}=0$, then $\braket{\phi|H|\phi}>\beta>\frac{1}{\poly(T)}$.

Since $H\in\spn\mathcal{G}_{XZ}$, we can write it as follows:
$$H=\sum_{S\in\mathcal{G}_{XZ}} d_S S= \sum_{S\in\mathcal{G}_{XZ}} |d_S|\sgn(d_S)S$$
We then scale the Hamiltonian.
$$D=\sum_{S\in\mathcal{G}_{XZ}}|d_S|$$
$$p_S=\frac{|d_S|}{D}$$
$$H'=\frac{H}{D}=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)S$$

@@

@@

We then follow \cite{mahadev_delegation}. That is, the server would commit copies of the ground state of the Hamiltonian for the classical client to measure.
The client would keep a single copy for output, and use the other copies to check whether the computation is done properly.

Take $p_0$ and $p_1$ to be the probability to measure $\sgn(d_S)\braket{\phi|S|\phi}=-1$ on $\ket\psi_{circuit}$ and $\ket\phi$ respectively, where $\phi$ is perpendicular to $\psi_{circuit}$. Obviously, $p_0=\frac{1}{2}$, and $p_1<\frac{1}{2}$... TODO Now what? Hypothesis testing...?

>>>>

Let $C$ be a circuit with the above properties. Define the following quantities.
\begin{itemize}
	\item $C=U_T\ldots U_1$
	\item Let $x$ be the circuit input. Which is classical.
	\item Let $y$ denote the initial state. That is, $x$ possibly concatenated with ancillaries.
	\item Let $y_i$ denote the $i$-th bit of $y$
	\item Let $n$ be the number of qubits in $C$
\end{itemize}

We then attempt to construct a local Hamiltonian with the following ground state that encodes the history of the computation: $$\psi_{circuit}=\sum_{t=0}^TU_t...U_1\ket{y}\otimes\ket{\hat{t}}$$
We do so by ensuring states perpendicular to it have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification is taken from \cite{PhysRevA.78.012352}.

@@

Then, we ensure that the initial condition is set up correctly.
$$H_{in}=\sum_{i=1}^n(I-\ket{y_i}\bra{y_i})\otimes\ket{0}\bra{0}_1$$
The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$. Furthermore, $H_{in}\in\spn\mathcal{G}_{XZ}$
$$H_{in}=\frac{1}{4}\sum_{i=1}^n(I-(-1)^{y_i}Z_i)\otimes(I+Z_1)$$

@@

Now we consider the kernels of the Hamiltonians we defined. Notice the following.
$$K_{clock}=\ker H_{clock}$$
$$K_{in}=\ker H_{in}$$
$$K_{prop}=\ker H_{prop}$$
$$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\psi_{circuit}}$$
We now consider the space outside the desired state.
$$S=(\spn\set{\psi_{circuit}})^\bot$$
$$H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$$
To combine the Hamiltonians, we apply the projection lemma twice.
$$\exists J_{clock}
=\frac{\poly\left(\norm{H_{in}\big|_S}\right)}{\lambda\left(H_{clock}\big|_{S\cap K^\bot_{clock}}\right)}
=O(n)=O(T)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}})-\frac{1}{8}$$
$$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
=\frac{O(n+T)}{\Omega(T^{-2})}=O(T^3)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$ to obtain the following properties.
\begin{itemize}
	\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
	\item $\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$ for $\ket\phi$ such that $\braket{\phi|\psi_{circuit}}=0$
	\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$. There are $O(T)$ nonzero components, whose coefficients are each at most $O(T^3)$.
\end{itemize}

@@

Given $\ket\phi$, now we're interested in the value of $\braket{\phi|H|\phi}$. Here we follow \cite{PhysRevA.93.022326}. Note that if $\phi=\psi_{circuit}$, then $\braket{\phi|H|\phi}=0$. If $\braket{\phi|\psi_{circuit}}=0$, then $\braket{\phi|H|\phi}>\frac{3}{4}$.

Since $H\in\spn\mathcal{G}_{XZ}$, we can write it as follows:
$$H=\sum_{S\in\mathcal{G}_{XZ}} d_S S= \sum_{S\in\mathcal{G}_{XZ}} |d_S|\sgn(d_S)S$$
We then scale the Hamiltonian.
$$D=\sum_{S\in\mathcal{G}_{XZ}}|d_S|$$
$$p_S=\frac{|d_S|}{D}=O(T^4)$$
$$H'=\frac{H}{D}=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)S$$

@@

Now let $\ket\phi$ be such that $\braket{\phi|\psi_{circuit}}=0$.
Take $p_0$ and $p_1$ to be the probability to measure $\sgn(d_S)\braket{\phi|S|\phi}=1$ on $\ket\psi_{circuit}$ and $\ket\phi$ respectively.
$$p_0=\frac{1}{2}$$
$$\braket{\phi|H'|\phi}=\frac{1}{O(T^4)}\braket{\phi|H|\phi}=\Omega(T^{-4})$$
$$\Rightarrow p_1=\frac{1}{2}+\Omega(T^{-4})$$

@@

We then follow \cite{mahadev_delegation}. That is, the server would commit copies of the ground state of the Hamiltonian for the classical client to measure.
The client would keep a single copy for output, and use the other copies to check whether the computation is done properly.
TODO Now what? Hypothesis testing...?
